Fast gravitational wave parameter estimation without compromises

### 2023-02-06 src/tex/ms.tex
Add Veitch and Ashton
Add sentences related to heterodyned likelihood

% Effort going to new tools development.
In order to address this, there are efforts from multiple groups to speed up the
PE process. This includes methods that employ modern techniques such as
using reduced-order quadrature\cite{Canizares:2014fya,Smith:2016qas}, leveraging adaptive proposal distribution in nested sampling
\cite{Williams:2021qyt}, deep learning networks pre-trained on large collections
of waveforms \cite{Dax:2021tsq,Dax:2022pxd}, as well as methods that reduce the
computational expense of classical PE by leveraging our knowledge of GW signals
\cite{Islam:2022afg,Roulet:2022kot,Lee:2022jpn,Lange:2018pyp,Wofford:2022ykb}.
While these avenues are promising for standard GW problems, they rely on
assumptions that may not hold for analyses targeting additional physical effects
beyond standard CBCs in GR, such as lensing and deviations from GR, or may use
approximations that do not compute the Bayesian likelihood exactly.

@@

To obtain a reference waveform, we currently use the \textsc{differential
evolution} algorithm \cite{Storn1997DifferentialE} available in the
\textsc{scipy} package \cite{2020SciPy-NMeth} to find the waveform parameters
which maximize the likelihood.  The reference waveform could also be produced
from trigger parameters precomputed by a search pipeline without additional
computation.

>>>>

% Effort going to new tools development.
In order to address this, there are efforts from multiple groups to speed up the
PE process. This includes methods that employ modern techniques such as
using reduced-order quadrature\cite{Canizares:2014fya,Smith:2016qas}, leveraging adaptive proposal distribution in nested sampling
\cite{Williams:2021qyt}, deep learning networks pre-trained on large collections
of waveforms \cite{Dax:2021tsq,Dax:2022pxd}, as well as methods that reduce the
computational expense of classical PE by leveraging our knowledge of GW signals
\cite{Veitch:2014wba,Ashton:2021anp,Islam:2022afg,Roulet:2022kot,Lee:2022jpn,Lange:2018pyp,Wofford:2022ykb}.
While these avenues are promising for standard GW problems, they rely on
assumptions that may not hold for analyses targeting additional physical effects
beyond standard CBCs in GR, such as lensing and deviations from GR, or may use
approximations that do not compute the Bayesian likelihood exactly.

@@

To obtain a reference waveform, we currently use the \textsc{differential
evolution} algorithm \cite{Storn1997DifferentialE} available in the
\textsc{scipy} package \cite{2020SciPy-NMeth} to find the waveform parameters
which maximize the likelihood.  The reference waveform could also be produced
from trigger parameters precomputed by a search pipeline without additional
computation. Once we obtained the reference waveform, we can check the accuracy
of the heterodyned-likelihood by comparing its value to the original likelihood
at several points in the parameter space. We can choose the number of bins such
that the difference between the values of the two likelihoods is smaller than
chosen tolerance threshold.
